Keccak Thesis

### 2018-03-27 s2018-math490/thesis/thesis.tex
Add outline
Signed-off-by: Alexander Scheel <alexander.m.scheel@gmail.com>

\begin{abstract}
    TODO
\end{abstract}

@@

@@

@@

@@

@@

@@

\subsubsection{Bijectivity} \label{sec:p:bijectivity}

\subsubsection{Order of the Permutation} \label{sec:p:order}

\subsubsection{Inverse of the Permutation} \label{sec:p:inverse}

\subsubsection{XOR ($\oplus$) Distributivity} \label{sec:p:xor}

\subsubsection{Generalizations of $\theta$ and $\chi$} \label{sec:p:generalizations}

\subsubsection{Choice of Parameters for $\theta$ and $\chi$} \label{sec:p:generalizations}

@@

@@

@@

@@

@@

@@

@@

@@

@@

>>>>

\begin{abstract}
    % TODO
    TODO
\end{abstract}

@@

% TODO
% More information about structure of analysis section.

@@

% TODO Outline
%    - Historic
%        - Ciphers vs Codes
%
%    - Modern
%        - Symmetric
%        - Asymmetric
%        - Hash Functions
%        - Building Protocols

@@

% TODO Outline
%   - Properties
%   - History of Development
%   - History of Attacks
%   - Modern Theory and Structure

@@

% TODO Outline
%    - Authors Background (keccak team)
%    - Function design goals
%    - NIST Contest
%    - NIST standardization controversy? (sources?)

@@

    SHA-3 consists of two parts: a core permutation function, KECCAK-$f$, and
a domain extender, the KECCAK sponge function.

% TODO Outline
%   - Sponge Function
%   - State Array
%   - Five functions
%   - Keccak-$f$

@@

% TODO Outline
%   - Outline following subsections

\subsection{Bijectivity} \label{sec:p:bijectivity}

% TODO Outline
%   - Reason why bijectivity is important
%   - Impact on attacks?

\subsubsection{Of $\theta$} \label{sec:p:b:t}

% TODO Outline
%   - Theta -> XOR with 11 different values; linear equations?
%   - What sizes are bijective?
%   - Discussion in literature

\subsubsection{Of $\rho$} \label{sec:p:b:r}

% TODO Outline
%   - Obvious permutation of bit orders

\subsubsection{Of $\pi$} \label{sec:p:b:p}

% TODO Outline
%   - Obvious: permutation of bit orders

\subsubsection{Of $\chi$} \label{sec:p:b:c}

% TODO Outline
%   - Harder, discussion in literature.

\subsubsection{Of $\iota$} \label{sec:p:b:i}

% TODO Outline
%   - Obvious: XOR with fixed value.

\subsection{Order of the Permutation} \label{sec:p:order}

% TODO Outline
%   - Outline why interesting
%   - Attack on PRF/XOF -> low cycle size
%   - Values over 2^(25w) indicate PRF has smaller upper bound for actual
%       entropy
%   - T R P C I

\subsection{Evaluation of the Orders of Composition of Permutations}

% TODO Outline
%   - w=1 evaluation
%   - Evaluation of different orderings of trpci

\subsection{Inverse of the Permutation} \label{sec:p:inverse}

% TODO Outline
%   - Outline simplification of f^{-1}
%   - Closed form for theta, chi
%   - Give algorithm for any w?

\subsection{XOR ($\oplus$) Distributivity} \label{sec:p:xor}

% TODO Outline
%   - Theta, Rho, Pi - free
%   - Chi, Iota - no
%   - Makes analysis harder, which is good

\subsection{Generalizations of $\theta$ and $\chi$} \label{sec:p:generalizations}

% TODO Outline
%   - Evaluation of effect?
%   - Pending eval?

\subsection{Choice of Parameters and Ordering of Composition} \label{sec:p:generalizations}
% TODO Outline
%   - Pending evaluation?

@@

% TODO Outline
%   - Overview of why it matters

@@

% TODO Outline
%   - Overview of why it matters - one round
%   - Can see effect of rho in w increasing
%   - Graphics

@@

% TODO Outline
%   - Graphics
%   - Impact of importance
%   - Show composition order impact if any?

@@

% TODO Outline
%   - Graphics
%   - Impact and importance

@@

% TODO Outline
%   - Importance
%   - Finding patterns hard
%   - No obvious connection for how to extend w=1 -> w=2
%   - Searches limited

@@

% TODO Outline
%   - Outline subsections

@@

% TODO Outline
%   - Probable due to order analysis
%   - Impact, attack

@@

% TODO Outline
%   - More probable
%   - Impact, attack

@@

% TODO Outline
%   - SHA-3 Secure, but introduces new attack vectors
%   - Need more in the way of LC for SHA-3-esq functions
%_  - Needs permutation-based cryptanalysis
%   - Differential cryptanalysis not likely to be of much use
